\beginsong {The British grenadier} \footnotemark[
ititle = {British grenadier (The)}]

\footnotetext {Chanson datant du XVIIème siècle. C'est la marche rapide régimentaire du Corps of Royal Engineers, des Grenadier Guards, de l'Honourable Artillery Company et du Royal Regiment of Fusiliers.}

\beginverse
 Some talk of Alexander
And some of Hercules,
Of Hector and Lysander 
And such great names as these.
But of all the world's great heroes
There's none that can compare.
With a tow, row, row, row, row, row, 
To the British Grenadiers.
\endverse

\beginverse
Those heroes of antiquity
Ne'er saw a cannon ball
Or knew the force of powder
To slay their foes withal.
But our brave boys do know it
And banish all their fears.
Sing tow, row, row, row, row, row, 
For the British Grenadiers.
\endverse

\beginverse
Whene'er we are commanded
To storm the palisades,
Our leaders march with fusees,
And we with hand grenades.
We throw them from the glacis,
About the enemies' ears.
Sing tow, row, row, row, row, row, 
The British Grenadiers.
\endverse

\beginverse
And when the siege is over,
We to the town repair.
The townsmen cry, "Hurrah, boys,
Here comes a Grenadier!
Here come the Grenadiers, my boys,
Who know no doubts or fears!"
Then sing tow, row, row, row, row, row,
The British Grenadiers.
\endverse

\beginverse
Then let us fill a bumper,
And drink a health to those
Who carry caps and pouches,
And wear the loupèd clothes.
May they and their commanders
Live happy all their years.
With a tow, row, row, row, row, row,
For the British Grenadiers.
\endverse

\endsong
