\beginsong{STRIKE THE BELL\footnotemark}[
ititle={Strike the bell}]

\footnotetext{Shanty découlant de la modification marine des paroles d'une chanson de Henry Clay Work, Ring the
	bell watchman (1865). L'appel s'adressant maintenant au second-maître pour qu'il sonne la fin du quart.
	Les marins Anglais, Allemands et Scandinaves chantent ce shanty.}

\beginverse
Out on the poop-deck an walking about,
There's the second mate so steady and so stout;
What hi is a-thinking of he doesn't know himsel'
We wish that he would hurry up and strike, strike the bell!
\endverse

\beginchorus
\textbf{Refrain}
\textit{Strike the bell, second mate, let us go below,
	Look well to wind'ard you can see it's going to blow;
	Look at the glass, you can see that it has fell,
	We wish that you would hurry up and strike, strike the bell!}
\endchorus

\beginverse
Down on the maindeck and working at the pumps,
There's the startboard watch all a-longing for their bunks;
Looking out to windward they see a great swell,
They're wishing that the second mate would strike, strike the bell!
\endverse

\beginverse
Aft at the wheel poor Anderson stands,
Grasping at the spokes with his cold mittened hands;
Looking at the compass, oh the course is clear as Hell,
He's wishing that the second mate would strike, strike the bell!
\endverse

\beginverse
Forward on the foc'sle head a-keeping sharp look-out,
Young Johnny's standing ready for to shout;
Lights ar burning bright, sir, and ev'ry thing is well,
He's wishing that the second mate would strike, strike the bell!
\endverse

\beginverse
Aft on the quaterdeck the gallant captain stands,
Looking out to winward a spyglass in his hand;
What he is a-thinking of we know very well,
He's thinking more of short'ning sail than striking the bell!
\endverse
\endsong