\beginsong{WHISKEY IN THE JAR} [
ititle={Whiskey in the jar}]

\beginverse
As I was going over the Kilmagenny mountain
I met with Captain Farrell and his money he was counting.
I first produced my pistol, and I then produced my rapier.
Sayin' : "Stand and deliver, for you are my bold deciever".
\endverse

\beginchorus
\textbf{Refrain}
Musha ring dumma do damma da
\bis{Whack fol the daddy, O,}
There's whiskey in the jar.
\endchorus

\beginverse
He counted out his money and it made a pretty penny,
I put it in my pocket and I gave it to my Jenny,
She sighed and she swore that she never would betray me,
But the devil take teh women, for they never can be easy.
\endverse

\beginverse
I went into my chamber all for to take a slumber,
I dreamt of gold and jewel and for sure it was no wonder.
But Jenny drew my charges, and she filled them up with water,
An' she sent for Captain Farrell, to be ready for the slaughter.
\endverse

\beginverse
And 't was early in the morning before I rose to travel,
The guards were all around me and likewise Captain Farrell,
I then produced my pistol, for she stole away my rapier,
But I couldn't shoot the water, so a prisoner I was taken.
\endverse

\beginverse
If anyone can aid me, 't is my brother in the army,
If I could learn his station, in Cork or in Killarney,
And if he'd come and join me, we'd go roving near Kilkenny,
I'll engage he'd treat me fairer than my darling sportling Jenny.
\endverse

\beginverse
Now some men take delight in the drinking and te roving,
But others take delight in the gambling and the smoking,
But I take delight in the juice of the barley,
And courting pretty Jenny in the morning bright and early.
\endverse
\endsong