\beginsong {The Ball of Kerrymuir} [
ititle= {Ball of Kerrymuir, the}]

\beginchorus
\textbf {Refrain}
Balls to your partner,
Arse against the wall.
If you’ve never been fucked
On a Saturday night
You’ll never be fucked at all.
\endchorus

\beginverse
’T was the gathering of the clans
And all the Scots were there
A-feeling up the lassies
Among the public hair.
\endverse

\beginverse
Four and twenty virgins
Came down from Inverness,
And when the ball was over
There were four and twenty less.
\endverse

\beginverse
There was fucking in the kitchen,
And fucking in the halls,
You couldn’t hear the music,
For the clanging of the balls.
\endverse

\beginverse
The village plumber, he was there
He felt an awful fool,
He’d come eleven leagues or more
And forgot to bring his tool.
\endverse

\beginverse
The village idiot he was there
Up to his favourite trick,
Boucin’ on his testicles,
And whistlin’ through his prick
\endverse

\beginverse
The village copper he was there,
He had a mighty tool,
He pulled his foreskin over his head,
And yodelled through the hole.
\endverse

\beginverse
The chimney sweeper, now he was there
But he soon got the boot
For every time he farted,
He filled the room with soot.
\endverse

\beginverse
The Mayor’s daughter, she was there
She had the crowd in fits,
A-jumping off the mantelpiece
And bouncing off her tits.
\endverse

\beginverse
Tiny Timmy, he was there
He was only eight,
He couldn’t reach the lassies,
So he had to masturbates.
\endverse

\beginverse
And when the ball was over,
They all went home to rest,
The music had been exquisite,
But fucking was the best.
\endverse

\endsong